Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-03 article.tex
typo
Start to speak about directivity

%  Partial correlation => Symmetric measure
Since this matrix is symmetric, it is not possible to infer the causal
mechanism behind the interaction (I directly causes J, J directly causes I or
both [de la Fuente, 2004]). Futhermore two other causal mechanisms may be implied
by a non-zero partial coefficient. First, the pair of variables may be induced
by a common (hidden) variable and second, I (respectively J) is conditionally
correlated to a hidden variable affecting J (resp. I) [de la Fuente, 2004].

% Introduce a custom solution to make the Y matrix asymmetric
% Introduce Filtering

% Introduce directivity

>>>>

Since the partial correlation is symmetric, it is not possible to infer the causal
mechanism behind the interaction (I directly causes J, J directly causes I or
both [de la Fuente, 2004]). Furthermore two other causal mechanisms may be implied
by a non-zero partial coefficient. First, the pair of variables may be induced
by a common (hidden) variable and second, I (respectively J) is conditionally
correlated to a hidden variable affecting J (resp. I) [de la Fuente, 2004].

% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
% TODO better link
%      add that we make the count matrix antisymmetric (count - count.T)
%      say that we normalize and stack
Some causal information (directivity of the links) were retrieved from the
data by comparing activity of each couple of neurons between two subsequent
time steps. The directivity method tries to detect variation of fluorescence
signal of a neuron $j$ due to a neuron $i$. This method counts the number of
times that $X_{t+1,j} - X_{t, i} \in [f_1, f_2]$ where $f_1$ and $f_2$ are
parameters of the method.
